---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# descriptiveR

<!-- badges: start -->
<!-- badges: end -->


The goal of descriptiveR is to make cleaning column names easier, it also helps you to create descriptive stats in a very friendly way..

## Installation

You can install the development version of descriptiveR from [GitHub](https://github.com/) with:

```{r}
# install.packages("devtools")
devtools::install_github("franc703/descriptiveR")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r}
library(descriptiveR)
```

When you have a data frame where the column names contain a prefix that you want to eliminate like in the mock dataframe I created below.


```{r example}
## basic example code
df <- data.frame(
pre_col1 = c(1,2,3),
pre_col2 = c(4,5,6)
)
```

Use `col_replace()` when you want to modify a common pattern across variable names.

```{r}
col_replace(df, "^pre_", "")
```

In this example we have remove the prefix `pre_` from the names of the columns.
